A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-19 paper/ch_potentials.tex
write on CCH-Pot

\todo{talk about CCH-Pot}

@@

>>>>

@@

\subsubsection{Three-Phase Setups}

Supporting live traffic is also possible with a three-phase setup:
A slow preprocessing phase, a faster \emph{customization} phase, and fast queries.
The customization phase is run regularly and incorporates updates to the weights into the auxiliary data.
CRP~\cite{dgpw-crprn-13} and Customizable CH~(CCH)~\cite{dsw-cch-15} follow this setup.
Luckily, a CCH is just a CH with some additional properties.
The CH in CH-Potentials can be replaced by a CCH without further modifications.
Thus, CCH-Potentials could also support a three-phase setup.
For applications which allow for a three-phase setup, CCH-Potentials are likely a better choice for supporting live traffic.
However, evaluating CCH-Potentials is beyond the scope of this paper.
We focus on evaluating CH-Potentials as a building block in the two-phase setup.
